Pool Model

### 2025-08-28 pool_model.tex
partially rewrite introductory part again

we expect to be able to simplify the problem and map it to a system of \acp{ode}.

@@

@@

To test the spatial limitations of the described above approach consider the system consisting from
two bacterial species that can be described by two internal states: lag and growth states.

@@

% ------------------------------------------------------------------------------------------------
\subsection{Constructing an Agent-Based Pool Model}
The previously considered \ac{ode} formulation makes extensive use of the assumption that the
bacteria are evenly distributed and all communications and interactions between bacteria or
nutrients occurr on time scales much faster than the remaining processes.
However, for heterogenous systems or nutrients with low diffusability, this assumption might not be
valid.\\
In order to construct a model which can encapsulate diffusion of nutrients and heterogeneity of
the bacteria or nutrients, we have to take into consideration the spatial component of our setup.
\acp{abm} force researchers to think in terms of cellular processes, thus bridging the gap from a
collective (bulk) model to an individual-based (single-cell) description.
The following sections will demonstrate how a given \ac{ode} system can be translated into a
custom-built \ac{abm} which has only a few more overall parameters.
To construct our \ac{abm}, we use \texttt{cellular\_raza}~\cite{Pleyer2025} which was designed to
provide maximal flexibility for researchers in order to construct minimalist models.
Without the ability to define and control the precise behavior of our cell-agents, the following
approaches would not be possible.

>>>>

we expect the \ac{ode} description to be valid.

@@

In order to construct a model which can encapsulate diffusion of nutrients and heterogeneity of
the bacteria or nutrients, we have to take into consideration the spatial component of our setup.
\acp{abm} force researchers to think in terms of cellular processes, thus bridging the gap from a
collective (bulk) model to an individual-based (single-cell) description.
We consider the system consisting from two bacterial species that can be described by two internal
states: lag and growth states.

@@

@@

% ------------------------------------------------------------------------------------------------
\subsection{Constructing an Agent-Based Pool Model}
The following sections will demonstrate how a given \ac{ode} system can be translated into a
custom-built \ac{abm} which has only a few more overall parameters.
To construct our \ac{abm}, we use \texttt{cellular\_raza}~\cite{Pleyer2025} which was designed to
provide maximal flexibility for researchers in order to construct minimalist models.
Without the ability to define and control the precise behavior of our cell-agents, the following
approaches would not be possible.
